\section{Broader Impact}

Developing neural systems with multiple levels of adaptivity --- development and learning, in addition to evolution --- is considered a major goal of EANN research \autocite{Downing2015IntelligenceSystems}.
By probing the relationship between evolution and learning potential, this research will contribute to the ongoing development of this next generation of EANN.
Today, EANN see commercial applications such as finance and ecommerce; applications will continue to expand as EANN mature.
EANN offer capabilities radically different from currently existing systems; evolving neural networks are suited to problem domains that are not suited to supervised learning such as robotics (i.e. grasping, bipedal walking, etc.) \autocite{Downing2015IntelligenceSystems} and can naturally be extended to perform online learning \autocite{Tonelli2013OnNetworks}.
The next generation of EANN promises to translate into tangible, pervasive, and profoundly innovative products and services.

This project will yield immediate, concrete contributions to the scientific community, as well.
Computational experiments will be implemented using the Modular Agent Based Evolution Framework.\autocite{Hintze2017Mabe}
This way, software components will be made available under a MIT license for easy, plug-and-play reuse by other researchers.
The techniques for evolving HPFIR ANN developed through this project are naturally extensible to many problem domains, such as game-playing agents, robot control, and image classification.
We plan to work with undergraduate researchers to demonstrate applications of such evolved networks and exploit Empirical to develop a web-based tool to evolve HPFIR ANN and export those networks in formats compatible with existing deep learning frameworks, (including Caffe, TensorFlow, Theano, and Torch) for further refinement.
We will pursue support through the NSF BEACON Center, which places dozens of underrepresented undergraduate students into evolution-focused research laboratories every summer, for an undergraduate research assistant.

% This research is especially applicable in terms of evolving EANN that can take advantage of potential for lifetime irregular refinement..
% As EANN become more capable and the cost of parallel computing power continues to decrease, EANN  will become ripe for applications in the technology sector.
% Commercial pioneers, such as  Sentient Technologies, are already investigating applications of EANN in fields such as e-commerce and finance [autocite].
% % EANN have the potential to offer capabilities distinct from neural network technology currently standard in industry.....
% In particular, the capability to train networks to do complex tasks that are not well suited to supervised learning and the potential for online learning in these systems  \autocite{Downing2015IntelligenceSystems} means the potential for systems that can interface socially with people....
% The disruptive products that EANN will lead to are difficult to predict, but they might include .....
% Commercialization of EANN, which will be accelerated by theoretical and methodological advances by EANN researchers, promises to make the unique capabilities of   consumers benefit from the unique capabilities offered by EANN.

% \begin{itemize}
%   \item artificial intelligence has direct applications to technology; stronger artificial intelligence has the potential to allow people to more fully exercise their human capacities
%   \item EANN techniques are starting to be used in industry (i.e.Sentient AI)
%   \item need to be more specific...
% \end{itemize}
